\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-10-20 fully-abstract-comp/popl2019/paper.tex
Update WBCF and LSE propety part to use LaTeX references

Ideally, we would like to define the properties in a way that is
\begin{enumerate}
\item {\itshape intuitive}
\item {\itshape useful for reasoning:} we should be able to use WBCF and LSE when reasoning about correctness and security of programs using \stktokens{}.
\item {\itshape reusable in secure compiler chains:} for compilers using \stktokens{}, one should be able to rely on WBCF and LSE when reasoning about correctness and security of other compiler passes and then compose such results with our results to obtain results about the full compiler. 
\item {\itshape arguably "complete"}: the formalization should arguably capture the entire meaning of WBCF and LSE and should arguably be applicable to any reasonable program.
\item {\itshape potentially scalable}: even though we currently do not consider dynamic code
  generation or multi-threading, the current formalization should at least potentially extend to such settings.
\end{enumerate}

Previous formalisations in the literature are formulated in terms of a static control flow graph~\cite[e.g., ]{Abadi2005Theory}.
While these are intuitively appealing (1), it is not clear how they can be used to reason about programs (2) or other compiler passes (3), they lack temporal safety guarantees (4) and do not scale (5) to settings with dynamic code generation (where a static control flow graph cannot be defined).
Skorstengaard et al. [2018] provide a logical relation that can be used to reason about programs using their calling convention (2,3), but it is not intuitive (1), there is no argument for completeness and it is unclear whether it will scale to more complex features.

>>>>

Ideally, we would like to define the properties in a way that is
\begin{enumerate}
\item {\itshape intuitive} \label{def-prop:intuitive}
\item {\itshape useful for reasoning:} we should be able to use WBCF and LSE when reasoning about correctness and security of programs using \stktokens{}. \label{def-prop:useful}
\item {\itshape reusable in secure compiler chains:} for compilers using \stktokens{}, one should be able to rely on WBCF and LSE when reasoning about correctness and security of other compiler passes and then compose such results with our results to obtain results about the full compiler. \label{def-prop:reusable}
\item {\itshape arguably "complete"}: the formalization should arguably capture the entire meaning of WBCF and LSE and should arguably be applicable to any reasonable program. \label{def-prop:complete}
\item {\itshape potentially scalable}: even though we currently do not consider dynamic code generation or multi-threading, the current formalization should at least potentially extend to such settings. \label{def-prop:scalable}
\end{enumerate}

Previous formalisations in the literature are formulated in terms of a static control flow graph~\cite[e.g., ]{Abadi2005Theory}.
While these are intuitively appealing (\ref{def-prop:intuitive}), it is not clear how they can be used to reason about programs (\ref{def-prop:useful}) or other compiler passes (\ref{def-prop:reusable}), they lack temporal safety guarantees (\ref{def-prop:complete}) and do not scale (\ref{def-prop:scalable}) to settings with dynamic code generation (where a static control flow graph cannot be defined).
\citet{skorstengaard_reasoning_2017} provide a logical relation that can be used to reason about programs using their calling convention (\ref{def-prop:useful},\ref{def-prop:reusable}) it is not intuitive (\ref{def-prop:intuitive}), there is no argument for completeness (\ref{def-prop:complete}), and it is unclear whether it will scale to more complex features (\ref{def-prop:scalable}).
